### 2016-11-15 paper/intro.tex
another pass on intro

As software evolves it is expected that the number of tests and the
length of test runs increase.  Both elements can add up to the
aggregate cost of running a test suite, which can lead to late reports
of test failures.  At large IT organizations, dealing with high
testing costs is a common problem.  The Google TAP
system~\cite{google-tap,google-ci} and the Microsoft CloudBuild
system~\cite{prasad-shulte-ieee-microsoft-ci} evidence the importance
of speeding up test execution in industry.  This problem, however, is
not specific to industrial giants like Microsoft and Google.  For
example, a recent paper from the automotive industry reported that
test suites can take days to run~\cite{artl-etal-icst2015}.

@@

Several approaches have been proposed in the literature to optimize
regression testing.  Research has focused mostly on test suite
minimization, prioritization, reduction, and
selection~\cite{yoo-harman-stvr2012}.  Although regression testing is
a recognized problem both in industry and academia, to the best of our
knowledge no prior work has investigated how prevalent the problem is
in open-source projects.  Renting a cloud
service\footnote{\url{https://clutch.co/cloud}}, or even building a
server farm (for increased security), is a popular approach to
mitigate the regression testing problem in large organizations.  This
alternative can be used irrespective of complementary approaches to
save testing costs (e.g., test selection).  For example, as of August
2013, the Groupon PWA system, which powers the \url{groupon.com}
website, included over 19K tests.  To run all those tests, Groupon
used a cluster of 4 computers with 24 cores
each~\cite{kim-etal-fse2013}.  This approach, however, is unlikely to
be attractive for open-source and lower-budget projects.

>>>>

As software evolves it is expected that the number of tests and the
length of test runs increase.  Both components can add up to the
aggregate cost of running a test suite, which can lead to late reports
of test failures.  Dealing with high testing costs is not uncommon at
large IT organizations.  The Google TAP
system~\cite{google-tap,google-ci} and the Microsoft CloudBuild
system~\cite{prasad-shulte-ieee-microsoft-ci} show that efficiently
building and testing the software are a critically important process
at Google and Microsoft.  The regression testing problem is, however,
not specific to industrial giants.  For example, a recent paper from
the automotive industry reported that test suites can take days to
run~\cite{artl-etal-icst2015}.

@@

Several approaches have been proposed in the literature to optimize
regression testing.  Research has focused mostly on test suite
minimization, prioritization, reduction, and
selection~\cite{yoo-harman-stvr2012}.  Although regression testing is
a recognized problem both in industry and academia, to the best of our
knowledge no prior work has investigated the regression testing
problem in open-source projects.  The alternative of renting a cloud
service\footnote{\url{https://clutch.co/cloud}} to automate testing or
even building a server farm (for increased security), can be a
legitimate approach to mitigate the regression testing problem at
large organizations.  Note that this alternative can be used
irrespective of complementary approaches to save testing costs (e.g.,
test selection).  For example, as of August 2013, the Groupon PWA
system, which powers the \url{groupon.com} website, included over 19K
tests.  To run all those tests under 10m, Groupon used a cluster of 4
computers with 24 cores each~\cite{kim-etal-fse2013}.  For open-source
projects and lower-budget projects, it is still important to run test
suites efficiently in commodity hardware.
